---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# accord

<!-- badges: start -->
<!-- badges: end -->

The goal of accord is to provide an interface to the Discord API.

## ROADMAP


## Installation
<!-- cran install
You can install the released version of accord from [CRAN](https://CRAN.R-project.org) with:

```{r eval = FALSE}
install.packages("accord")
```
-->

You can install the development version of accord from GitHub with
```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("tanho63/accord")
```


## Usage

## Other Works

There are a few implementations of Discord API functions at the moment:

- [discordr](https://github.com/jljsio/discordr/) by Jordan Love seems to provide the ability to post messages via webhook. Only on GitHub.
- [Pirate](https://github.com/TheOnlyArtz/Pirate) by Amit Katz wraps more of the API and data models but is less maintained, uses R6, and doesn't seem to have much documentation (?)

## Code of Conduct
  
Please note that the accord project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
